### 2014-03-20 proceedings/tracks.tex

\documentclass[letter]{article}
\special{papersize=8.5in,11in}
\usepackage{fullpage}

@@

\newcommand\asdf[2]{\vspace{0.15in} \item {\Large \bf \sf #1}

{\large \em #2}}
\newcommand\keywords[1]{

@@

\track{1}{Official 2012 Apocalypse Track}

\begin{enumerate}
\asdf{An Eschatological Approach: The Four Horsemen of Computer Science}
{The Reverend Nicolas A. Feltman and Joan E. Chao, Mother Supremum}
\keywords{Eschatology, Horsies, Indulgences}
\asdf{World Domination Through the Use of a Graphical Reduction of the Six Degrees of Separation Concept with Potential Robot Design for Mode of Implementation}
{L. S. Berg and P. J. Barton}
\keywords{Six Degrees of Separation, Kevin Bacon, Turtle Power, World Domination, Bad Cartoon Jokes, Topology, Reduction, Depression, Graphical Model Abuse}
\end{enumerate}

@@

\track{2}{Comestibility theory}

\begin{enumerate}
\asdf{Food for Thought: Dining Philosophers}{}
\keywords{hunger-driven devices, morsels, monads}
\asdf{Higher-Order Generalized Algebraic Pizzas}
{Brandon Bohrer and Samir Jindel}
\keywords{Curry-Pepper Isomorphism, Grease Monad, Monoids in the Category of Delicious, $A^\flat$ Mixolydian}
\vspace{-0.1in}
\asdf{Lollipops and Lemma Drops: the sweet, sweet logic of candy}
{William Lovas}
\asdf{Algorithms for k/n Power-Hours}
{Ben Blum, Dr. William Lovas, Ph.D., Chris Martens, and Dr. Tom Murphy VII, Ph.D.}
\keywords{alcohol in computer science, algorithms for the real world, chemically-assisted reasoning, drinking game theory, hyper-driven devices}
\end{enumerate}

@@

\track{3}{Brought to you by the letter\dots}

\begin{enumerate}
\setcounter{enumi}{-1}
\asdf{TBD}
{Taus Brock-Nannestad and Gian Perrone}
\keywords{all is well here, send money, love to you and yours}
\asdf{The Letter}
{Frederick J. Mesp\"{u}tchy}
\asdf{Proof of P = NP}
{Samir Jindel and Brandon Bohrer}
\asdf{An Epistolary Reconstruction of the Curry-Howard Correspondence}
{Ben Blum and Michael Sullivan}
\keywords{Corre-Howard-Spondence, Simply Typed Lambada Calculus, Supernatural Deduction}
\asdf{The Kardashian Kernel}
{David F. Fouhey and Daniel Maturana}
\keywords{Kardashian, Kim, Kourtney, Khloe, Kernel, Kuadratic, Konvex, Koncave, Krylov, Kronecker, Kolmogorov, Karush-Kuhn-Tucker, K-Means, K-Armed-Bandit, Kohonen, Karhunen-Loeve, Kriging, Kalman, Kinect, Kovariance, Kurse-of-dimensionality, Kurvature, K-Nearest-Neighbor}
\end{enumerate}

@@

\track{4}{Did you bring enough to reshare \\ with the class?}

\begin{enumerate}
\setcounter{enumi}{-1}
\asdf{Implications of Constrained Thought Expression Achieved via a One Hundred-forty Character Message Limitation Applied to Complex Social Netwo}
{Nathan Brooks and Tommy Liu}
\keywords{\#socialmedia, \#sm, \#140}
\asdf{The Spineless Tagless Tweet Machine: Distributed Cloud-Based Social Crowdsourced Lazy Graph Reduction on the Web 2.0}
{Michael Sullivan}
\asdf{SIGBOVIK 2012 Take-Home Midterm Examination}
{James McCann}
\asdf{The National Month Of Pushing Spacebar}
{Tom Murphy VII}
\keywords{C++harles D:{\textbackslash}ickens, fanfic, repetitive stress injury, 2012: A Space Odyssey}
\asdf{What Most Medical Students Know About Computer Science}
{Brian R. Hirshman}
\keywords{computer science, electronic medical records, all-knowing doctors, important stuff, take two kilobytes and see me in the morning, dude we're too busy learning other things}
\end{enumerate}

@@

\track{5}{Programming languages research and \\ other games for children}
\begin{enumerate}
\asdf{Modeling Perceived Cuteness}
{Nathan Brooks and Evelyn Yarzebinski}
\keywords{cute, puppy, kitten, turtle, spider, snake, dog, cat, gecko, hamster}
\asdf{i-PHONE app stor : where is my pants}
{Dr. Tom Murphy VII, Ph.D. and Dr. Abigale G. Lade, Ph.D.}
\keywords{pants, where, is my, juvenilia}
\asdf{An Extensible Platform for Upwards and Sidewards Mobility}
{David Renshaw}
\asdf{A modern optimizing compiler for a dynamically typed programming \\ language: Standard ML of New Jersey (preliminary report)}
{Ian Zerny}
\asdf{Programming Language Checklist}
{Colin McMillen, Jason Reed, and Elly Jones}
\end{enumerate}

@@

\track{6}{Protect yo' shit}
\begin{enumerate}
\asdf{Cryptographically-Strong Hashing with Physics}
{James McCann and Fake Otherauthor}
\asdf{The Physics-Based Hashes of Twelve Really Good Ideas}
{Patent Troll}
\asdf{A modest proposal for the purity of programming}
{Robert J. Simmons and Tom Murphy VII}
\keywords{the next 700 terrible programming languages, hyper-driven devices, types}
\asdf{Preparation-Hom as the ideal completion of a Hemorrhoidal category}
{Sitsin C{\o}mfort and Minr{\o}v G{\o}rondt}
\keywords{hemorrhoids, fistulads, co-fistulads, push outs}
\asdf{A Randomized Commit Protocol for Adversarial - Nay, Supervillain - \\ Workloads}
{Ben Blum}
\keywords{two-phase, two-face, randomized algorithms, acid}
\asdf{Address space content randomization: exploit mitigation through data \\ randomization}
{Carlo Angiuli}
\keywords{security, optimization, nondeterministic memory, lower is better}
\end{enumerate}

>>>>

\documentclass[letter]{article}
\special{papersize=8.5in,11in}
\usepackage{fullpage}
\usepackage{fontspec}
\usepackage{amsfonts}

\setmainfont{Rumsey}
\setsansfont{TragicSans}

@@

\newcommand\paper[2]{\vspace{0.15in} \item {\Large \bf \sf #1}

{\large \em \sf #2}}
\newcommand\keywords[1]{

@@

%\track{8}{Take The Quiz: Which Pointless Time-Wasting Amusement are You?}
\track{8}{How to Keep Adults Busy and Other Fun Games for Children}

\begin{enumerate}
\paper{How to Keep a Graduate Student Busy}
{Paul Stansifer}
\keywords{all, work, and, no, play, makes, paul, a, dull, boy}
\paper{New Results in $k/n$ Power-Hours}
{Dr. Tom Murphy VII Ph.D.}
\keywords{generalized binge drinking, maths, finite-state automata, abstract interpretation}
\paper{Linear Logic Free}
{Carlo Angiuli}
\keywords{linear logic, free to play, app store}
\paper{It Still Seems That Black Has Hope in These Extremely Unfair Variants of Chess}
{Dr. Tom Murphy VII Ph.D., Ben Blum, and Jim McCann, in italics ...... oh! .... nervous laughter .... no, that's not part of the name still. I stopped saying the name. Why are you still typing? This isn't the name any more. End quote.}
\keywords{chess, stratego, guess who, clue, candy crush saga, game-tree search, combinations}
\end{enumerate}

@@

%\track{88}{Epic Local News You'll Be Sad You Missed}
\track{88}{Concerning Local Affairs}

\begin{enumerate}
\paper{PARTIAL TRANSCRIPT OF DEAN'S SPEECH TO THE FACULTY OF THE MELLON COLLEGE OF SCIENCES}
{Clint Falamenos}
\keywords{news, lane center, college of sciences}
\paper{Analysis of the Effects of Substantial Lane Closure During Afternoon Peak Along a Heavily-Traveled Urban Arterial Choke-Point}
{Nicholas Fudala}
\keywords{knowledge, pagers, RATPAG}
\paper{Yet Another Application of Our Pet Technique}
{Chester Francis and Nicholas Fudala}
\keywords{complexity, multiple patents pending, nobel peace prize}
\paper{Please Don't Let Open House Destroy the Universe}
{Jenn Landefeld}
\keywords{open house, destruction of universe, herding cats}
\end{enumerate}

@@

%\track{888}{Four Unbelievable New Theoretical Perspectives}
\track{888}{New Theoretical Perspectives}

\begin{enumerate}
%\setcounter{enumi}{-1}
\paper{Heterotopy Type Theory: \\ A Defense of the Traditional Foundations of Mathematics}
{Thomas Cramer and Sam Yeager}
\keywords{heterotopy type theory, identity type, freedom of expression axiom}
\paper{The Dumping Lemma - Assessing Regularity}
{Naomi Saphra}
\keywords{computational scatology, formal languages, poop jokes}
\paper{Statistical Watch Optimization}
{Bryce Summers}
\keywords{Watch, clock, time, probability, statistics}
\paper{A Simple Category-Theoretic Understanding of Category-Theoretic Diagrams}
{Stefan Muller}
\keywords{category, diagram, functor, diagram diagram}
\end{enumerate}

@@

%\track{8,888}{Three Important Ways to Stay Safe This Research Season}
\track{8,888}{Stay Safe Out There}

\begin{enumerate}
%\setcounter{enumi}{-1}
\paper{Cryptographically-Sound Jokes}
{Jim McCann}
\keywords{jokes, sha, md5}
\paper{DollarCoin: A Cryptocurrency with Proof-of-Dollar}
{Patrick J. Xia}
\keywords{cryptocurrency,
bitcoin,
dollars,
bills,
gamechanger,
disrupt,
awesome,
supercool,
thebest,
hashtag}
\paper{Towards a Completely Autonomous Vehicle}
{Nicholas Fudala and Chester Francis}
\keywords{pain, suffering, frustration}
\end{enumerate}

@@

%\track{88,888}{Improve Your Own Research With These Five Weird Tricks}
\track{88,888}{Easier, Better, Faster, Stronger Research Methodologies}
\begin{enumerate}
\paper{Belief-Sustaining Inference}
{Alex Reinhart and Jerzy Wieczorek}
\keywords{uninformative likelihood,
statistics,
embarrassment,
cognitive dissonance,
inference}
\paper{Solutions to Ley Line Access in Occult Computing}
{Maija Mednieks}
\keywords{ley lines,
occult computing,
miskatonic university,
installing linux on a dead badger,
playing god}
\paper{Measuring Your $\mathbb{P}$-ness: Determining How Like a Probability Distribution a Given Mathematical Object Is}
{John T. Longwood}
\keywords{lowbrow humour,
probability,
statistics}
\paper{a clarification of terminology}
{David Renshaw}
\keywords{did you mean,
search instead for,
not to be confused with}
\paper{What, If Anything, is Epsilon?}
{Dr. Tom Murphy VII Ph.D.}
\keywords{computational archaeology,
epsilon,
very-small and medium-small numbers}
\end{enumerate}

@@

%\track{888,888}{These New Ways to Program Will Blow Your Mind}
\track{888,888}{Innovations in Natural and Unnatural Languages}
\begin{enumerate}
\paper{IRS-1040-Based Computing: The Untapped Computational Power of Bureaucracy}
{William Gunther and Brian Kell}
\keywords{unconventional computation,
taxes,
compilers,
bureaucracy}
\paper{Towards Fooling and Foiling the NSA: \\
Surveying the State of Steganographic Programming Languages}
{Wolfgang Richter and Debjani Biswas}
\keywords{steganography,
esoteric programming language,
esoteric,
programming languages,
obfuscation,
cryptography,
shit}
\paper{Pikachu, Domosaur, and other Monolexical Languages}
{Sarah Allen, Jesse Dodge, and Domosaur Domosaur}
\keywords{natural language processing,
regular languages,
translation}
\paper{Unit-Test-Based Programming}
{Miguel \'{A}. Lech\'{o}n}
\keywords{unit test,
automatic stubbornness,
holy grail}
\end{enumerate}
